Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-27 Chapter-2/2-LArTPCs.tex
s

LArTPCs use  hermetically sealed and leak-checked vessels to abate the leakage and diffusion of contaminants into the system. The liquid argon filling of the volume occurs after the vessel is evacuated or purged with gaseous argon \textcolor{red}{[205]} to reduce remaining gases in the volume. Even so, the construction of a pure tank of argon is unviable, as several sources of impurity remain.  In particular, impurities can come from the raw argon supply, the argon filtration system and from the outgassing from internal surfaces. Outgassing is a continuous diffusive process  producing contaminants, especially water, even after the vessel is sealed, particularly from materials in the ullage region\footnote{.  While the liquid argon low temperature reduces outgassing in the liquid, this process remains significant for absorptive material (such as plastic) above the surface of the liquid phase}.  Since research-grade argon comes from the industrial distillation of air, the impurities with the highest concentration are nitrogen, oxygen and water, generally maintained under the 1 part per million level by the vendor.  Even so, a higher level of purity is necessary to achieve a free electron life time usable in meter scale detectors. Thus, argon  is constantly  filtered in the cryogenic system, which reduce the oxygen and water contamination to less than 100 parts per trillion. The filtration system depends on the size and drift distance of the experiment and, for experiments on several meters scale, it includes an argon recirculation system.

@@

\subsubsection{Recombination Effect}
After production, ionization electrons thermalize with the surrounding medium and may recombine with nearby ions. Recombination might occur either between the electron and the parent ion through Coulomb attraction (Onsager geminate theory  [2] ) or thanks to the collective charge density of electrons and ions from multiple ionizations in a cylindrical volume surrounding the particle trajectory (Jaffe[3]  columnar model ). 
Consideration on the  average electron-ion distance and the average ion-ion distance for argon show that the probability of geminate recombination is low; thus recombination in argon is mainly due to collective effects\cite{1748-0221-8-08-P08005}.  Since protons, kaons and stopping particles present a higher ionization compared to MIPs, recombination effects are more prominent when considering the reconstruction of energy deposited by these particles.

Models for a theoretical descriptions of recombination base on are provided in (Birks model [6]) and in (Box model [7]). The Birks model assumes a gaussian spatial distribution around the particle trajectory during the entire recombination phase and identical charge mobility for ions and electrons. The Box model also assumes that electron diffusion and ion mobility are negligible in liquid argon during recombination
In these models, the fraction of ionization electrons surviving recombination is a function of the number of ion-electron pairs per unit length, the electric field, the average ion-electron separation distance after thermalization and the angle of the particle with respect to the direction of the electric field -- plus the diffusion coefficient in the Birks model. Given the stringent assumptions, it is perhaps  not surprising that these models are in accordance to data only in specific regimes: the Birks model is generally used to describe recombination for low dE/dx, the Box model for high dEdX.
In LArTPC, the ICARUS and ArgoNeut have measured recombination in [8] and \cite{1748-0221-8-08-P08005} respetively. Since LArIAT uses the refurbished ArgoNeut TPC and cryostat,  LArIAT currently corrects for recombination using the ArgoNeut measurement, shown in figure \textcolor{red}{find figure}.

>>>>

LArTPCs use  hermetically sealed and leak-checked vessels to abate the leakage and diffusion of contaminants into the system. The liquid argon filling of the volume occurs after the vessel is evacuated or purged with gaseous argon \cite{1748-0221-9-07-P07005} to reduce remaining gases in the volume. Even so, the construction of a pure tank of argon is unviable, as several sources of impurity remain.  In particular, impurities can come from the raw argon supply, the argon filtration system and from the outgassing from internal surfaces. Outgassing is a continuous diffusive process  producing contaminants, especially water, even after the vessel is sealed, particularly from materials in the ullage region\footnote{While the liquid argon low temperature reduces outgassing in the liquid, this process remains significant for absorptive material (such as plastic) above the surface of the liquid phase.}.  Since research-grade argon comes from the industrial distillation of air, the impurities with the highest concentration are nitrogen, oxygen and water, generally maintained under the 1 part per million level by the vendor.  Even so, a higher level of purity is necessary to achieve a free electron life time usable in meter scale detectors. Thus, argon  is constantly  filtered in the cryogenic system, which reduce the oxygen and water contamination to less than 100 parts per trillion. The filtration system depends on the size and drift distance of the experiment and, for experiments on several meters scale, it includes an argon recirculation system.

@@

\subsubsection{Recombination Effect}
After production, ionization electrons thermalize with the surrounding medium and may recombine with nearby ions. Recombination might occur either between the electron and the parent ion through Coulomb attraction, according to Onsager geminate theory  [2], or thanks to the collective charge density of electrons and ions from multiple ionizations in a cylindrical volume surrounding the particle trajectory, according to Jaffe[3]  columnar model. 
Consideration on the  average electron-ion distance and the average ion-ion distance for argon show that the probability of geminate recombination is low; thus recombination in argon is mainly due to collective effects\cite{1748-0221-8-08-P08005}.  Since protons, kaons and stopping particles present a higher ionization compared to MIPs, recombination effects are more prominent when considering the reconstruction of energy deposited by these particles.

Models for a theoretical descriptions of recombination based on the Birks model and the Box model are provided in [6] and  [7] , respectively. The Birks model assumes a gaussian spatial distribution around the particle trajectory during the entire recombination phase and identical charge mobility for ions and electrons. The Box model also assumes that electron diffusion and ion mobility are negligible in liquid argon during recombination.
In these models, the fraction of ionization electrons surviving recombination is a function of the number of ion-electron pairs per unit length, the electric field, the average ion-electron separation distance after thermalization and the angle of the particle with respect to the direction of the electric field -- plus the diffusion coefficient in the Birks model. Given the stringent assumptions, it is perhaps  not surprising that these models are in accordance to data only in specific regimes: the Birks model is generally used to describe recombination for low dE/dx, the Box model for high dEdX.
In LArTPC, the ICARUS and ArgoNeut have measured recombination in [8] and \cite{1748-0221-8-08-P08005} respetively. Since LArIAT uses the refurbished ArgoNeut TPC and cryostat,  LArIAT currently corrects for recombination using the ArgoNeut measurement, shown in figure \textcolor{red}{find figure}.
